Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-12 docs/msr.tex
quering in a programming fashion.
added paper title

\title{TBA - software evolution, security defects oriented}

@@

@@

@@

\subsection{Data Provenance and Processing}

@@

>>>>

\title{Dismal Code: Studying the Evolution of Security Vulnerabilities}

@@

A security-related bug is a programming error that introduces a potentially
exploitable weakness into a computer system. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. One of the most common
approaches to identify software vulnerabilities is {\it static analysis}. This
kind of analysis is performed by automated tools either on the program's source
or object code and without actually executing it.

@@

\section{Related Work}

Cite this~\cite{ZAH11}.

@@

\subsection{Data Provenance and Processing}
\label{sec:data}

@@

\subsection{Experiment}
\label{sec:exp}
